Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-09-04 tex/test-WW-type-00z.tex
tex

The 6 leading--twist TMDs 
$f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a}$
and 2 leading--twist FFs $D_1^a, \; H_1^{\perp a}$ provide a basis
in the sense that in WW-type approximation all other TMDs and FFs 
can either be expressed in terms of these basis functions or vanish.
Below we shall see that, under the assumption of the validity of WW-type 
approximations, it is possible to express all SIDIS structure functions
in terms of the basis functions. \AP{Notice that SIDIS alone is of course not sufficient to determine
   the basis functions uniquely because the 8 basis functions appear
   in 6 SIDIS leading-twist structure functions. It is crucial to take advantage of
   other processes (such as Drell-Yan and hadron production in
   $e^+e^-$ annihilation, which are indispensable for the determination
   of $f_1^a$ and $D_1^a$).}
%\AP{Notice that SIDIS alone is of course not sufficient to determine the basis
%functions uniquely: the 8 basis functions appear in 6 \AP{leading-twist} SIDIS structure functions.
%It is crucial to take advantage of other processes: Drell--Yan for PDFs and TMDs
%and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
%play also important roles.}
%Notice that SIDIS alone is of course not sufficient to determine the basis
%functions uniquely: \AP{8 twist-2 TMDs (or 6 ``basis'' TMDs) and 2 twist-2 TMD FFs appear in 15 structure functions (8 twist-2 and 5 sub-leading). 
%Definitely hadron production in $e^+e^-$ annihilation data is needed, each FF couples with 4 different twist-2 TMD PDFs, and so for each FF we have a case with 5 unknowns accessible in 4 twist-2 observables.
%It is crucial to take advantage of  Drell--Yan process for TMDs
%and other processes 
%play also important roles.}

These basis functions allow us to describe, in WW-type approximation,
all other TMDs. The experiment will tell us how well the approximations work.
In some cases, however, we know in advance that the WW-type approximations 
have limitations, see next Section~\ref{Sec-3.8:limitations}.

>>>>

The 6 leading--twist TMDs 
$f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a}$
and 2 leading--twist FFs $D_1^a, \; H_1^{\perp a}$ provide a basis
in the sense that in WW-type approximation all other TMDs and FFs 
can either be expressed in terms of these basis functions or vanish.
Below we shall see that, under the assumption of the validity of WW-type 
approximations, it is possible to express all SIDIS structure functions
in terms of the basis functions\footnote{\AP{Notice that SIDIS alone is of course not sufficient to determine
   the basis functions uniquely because the 8 basis functions appear
   in 6 SIDIS leading-twist structure functions. It is crucial to take advantage of
   other processes (such as Drell-Yan and hadron production in
   $e^+e^-$ annihilation, which are indispensable for the determination
   of $f_1^a$ and $D_1^a$).}}.
These basis functions allow us to describe, in WW-type approximation,
all other TMDs. The experiment will tell us how well the approximations work.
In some cases, however, we know in advance that the WW-type approximations 
have limitations, see next Section~\ref{Sec-3.8:limitations}.
